\section{Chapter 3: Steam Distribution}
In industries, steam is mostly used for heating purposes. We are aware that there are two different types of steam: saturated steam and superheated steam. Process industries employ saturated steam. In order to produce energy, steam turbines primarily employ superheated steam. The steam boiler burns fuel or gas to produce steam. Through the pipes, steam is distributed to the process. The machine then uses the steam.

\subsection{Accessories for Steam System}

\subsubsection{Strainer}
A strainer valve is a type of pipe fitting used to purify, filter, or separate liquid from solids while still allowing the liquid to flow through it. Most often, strain is employed to remove steam from a stream of mixed liquids.

\subsubsection{Pipe}
A pipe transports pressurized steam from a boiler to the functional components, like the steam engine or turbine. Such piping generally incorporates valves to control the flow of the steam or to stop it entirely.

\subsubsection{Moisture Separator}
Air with moisture is sent from the cooler to the separator. The is twirled around in air. As it is accelerated through it, a diffuser propels the separator's body. rotating force causes water droplets to hit the separator wall, where they are then gravitationally collected.

\subsubsection{Thermodynamic Trap}
The thermodynamic trap is a steam trap that operates simply but is exceptionally long-lasting. The trap works by utilizing the dynamic action of flash steam as it passes through the trap.

\subsubsection{Ball Float Trap}
Traps having a wide range of uses. Condensate loads of any weight can be efficiently handled. little in scale. Because of the high and continuous discharge capacity, maximum heat transfer is guaranteed. A ball float steam trap is the best solution for draining plants with automatic temperature control.

\subsubsection{PRV}
In spite of changes in demand and/or upstream (inlet) water pressure, a pressure-reducing valve (PRV) is an automatic control valve created to reduce higher unregulated input pressure to a constant, reduced downstream (outlet) pressure.

\subsubsection{Safety Valve}
Steam systems typically employ safety valves for downstream pressure-reduction devices and boiler overpressure protection, among other uses. Safety valves are used in process operations to prevent product damage due to excessive pressure even though their primary purpose is to ensure safety.

\subsubsection{Deaerator Head}
The current boiler feed water tank now has a Deaerator Head addition that has mixing nozzles for new make-up water, flash steam, and plant area condensate. The stainless-steel perforated mixing pipe is immersed in feed water. This makes it possible for the feed water tank to uniformly mix hot condensate, flash steam, and make-up water.

`'