\section*{Acknowledgement}
 
At first all praise to the Almighty Allah, the most merciful and beneficent, who has given us the strength, knowledge and ability to complete this report. 

Authors express their deepest revere, heartiest gratitude and produce respect to their faculty supervisor \textbf{Md Manirul Islam}, Department of Mechatronics Engineering, Rajshahi University of Engineering \& Technology, for his valuable guidance, continuous support, and constructive suggestions throughout the attachment period. His insightful comments and suggestions have been invaluable in shaping this report.

All the honorable teacher of Mechatronics Engineering Department, RUET, will forever remain the memories of the authors for their inspiration. 

We would like to express our gratitude to our parents for their continuous support and encouragement throughout our academic journey. We would like to thank our industry supervisor, \textbf{Engineer Md. Jainal Abedin} (EEE, RUET-04), Manager-Steam System \& Control Instrumentation of Forbes Marshall, for his guidance and support in ensuring the success of our attachment at Forbes Marshall Private Limited. We would also like to thank the staff at Renaissance Apparel Ltd. for their assistance and cooperation during our attachment. Finally, we would like to thank our friends and classmates for their support and encouragement throughout this journey.

\begin{flushright}
    \textbf{Avik Md Emtiaz Arefin}\\
    \textbf{id: 2008013}\\
    \textbf{Md Raihanul Haque Rahi}\\
    \textbf{id: 2008011}\\
    \textbf{Nazib Abrar}\\
    \textbf{id: 2008026}\\
    Rajshahi University of Engineering \& Technology, Rajshahi - 6204\\
    % TODO
    Date: December 3, 2024  
\end{flushright}

 
 
 
 
 
